\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-08-17 manuscript/main.tex
modified:   manuscript/main.aux 	new file:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

The listing service of China's real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries. Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references. Face-to-face interactions remain crucial for transactions. Additionally, Chinese government imposes stringent restrictions on the upper and lower limits of online listing prices, leading to a reluctance among sellers to list their properties online. This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties. Moreover, the China's real estate brokerage market operates under a bilateral agency model, resulting in lower transaction efficiency compared to the United States brokerage market. In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices. Conversely, in China, sellers have more freedom to set arbitrary listing prices in the offline market. It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.

Even though the China's real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China. Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. In 2014, Beke introduced a strategic initiative called the Agent Cooperation Network (ACN), which aims to integrate and share resources across its various subsidiaries. This strategy enables the realization of multiple revenue streams simultaneously, thereby optimizing operational efficiency and enhancing overall economic performance.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Moreover, in 2018, Lianjia decided to enhance its Agent Cooperation Network (ACN) strategy by incorporating smaller brokerages into its network and launching franchise stores under the brand name Deyou, along with other smaller formats. This strategic move aimed to increase network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

@@

In the real estate market, real estate is not a homogeneous good, and therefore, the brokerage market is characterized by a large number of firms with no significant barriers to entry. Traditional economic theory suggests that such a market, characterized by substantial competition, numerous firms, and low market concentration, is consistent with real-world observations. For example, Lianjia's offline stores account for less than 5\% of the total, yet Lianjia handles about 20\% of the national transactions. In addition, many well-known agencies, such as Woaiwojia and Centaline Property Agency, operate in this market, indicating a monopolistic competitive environment.

However, when looking at local segmented markets, the monopolistic competition model seems less applicable. In local markets, surrounding neighborhoods share similar community characteristics and public resources. Especially in China's real estate market, most properties are apartments, where the inherent differences between properties are minimal, making them relatively homogeneous goods. In addition, local real estate markets have no barriers to entry or exit, closely resembling perfect competition. From a cost perspective, the real estate market has undergone platform mediated reforms, where data resources have zero marginal cost characteristics and operating costs decrease as the user base expands, suggesting characteristics of a natural monopoly. Under these conditions, the operating position of firms differs significantly from that in a monopolistically competitive market. Due to network effects, an increase in the number of branches of a dominant real estate agency attracts more users, which in turn attracts more real estate listings. This positive feedback loop reinforces the dominant position of firms like Lianjia, leading to the formation of oligopolistic firms. These oligopolistic firms can further maintain their dominant market positions.

In local segmented markets, oligopolistic firms are responsible for increasing network strength and have significant market power. In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale. The environment of free entry, rapid technological progress, and business model innovation leads to an inclusive competitive landscape in the real estate brokerage market. This environment allows oligopolistic firms to either enhance the strength of their network effects or have their dominant positions challenged. As a result, monopolistic structures emerge from and are subsequently disrupted by competition, allowing real estate intermediaries to continuously evolve and drive the industry's rapid growth. The practical implication is that a competitive oligopolistic structure does not inherently impede competitive efficiency. Instead, as our empirical findings indicate, the enriched entry and transformations within the market lead to an increase in the number of transactions and house tours. This type of market structure can enhance firm efficiency, thereby facilitating more efficient transactions for buyers and sellers and improving overall market welfare, even though it may impede individual seller welfare.

As our empirical results show, Lianjia's strategy has significantly enhanced its network strength within segmented markets. From this perspective, the enhancement of network effects further drives the segmented market toward an oligopolistic competitive structure, which could increase the market welfare and facilitate the transactions between buyers and sellers. Moreover, with the development of online platforms and new technologies, such as Lianjia's latest VR home viewing technology, these network effects are gradually shifting from local networks to a global network. As a result, this development is shaping the overall market into an oligopolistic competition model on a larger scale.

In the future, as the network effects intensify, the real estate brokerage market may witness a more pronounced consolidation of market power among a few dominant players. This consolidation can lead to increased efficiencies through economies of scale and scope, where firms leverage their vast data resources and technological advancements to optimize operations and enhance consumer experiences. However, this shift also raises important considerations for regulatory bodies to ensure that the market remains competitive and accessible. The dynamic interplay between technological innovation and market structure will be crucial. As firms like Lianjia continue to innovate, incorporating artificial intelligence, big data analytics, and blockchain for secure transactions, the real estate market could become more transparent and efficient. These advancements could lower transaction costs, reduce information asymmetry, and provide consumers with more personalized services. Furthermore, the global reach of network effects implies that real estate brokerage markets across different regions might become more interconnected. This interconnectivity can facilitate cross-city or cross-province investments and diversify property portfolios for investors, contributing to a more resilient real estate market.

In conclusion, the evolution of the real estate brokerage market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges. From our empirical findings, this type of market structure can not impede the competitive efficiencies but policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants. This balanced approach will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.

>>>>

The listing service of China's real estate market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries. Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where suits are typically situated far apart, the role of offline real estate stores is minimized.\footnote{\citet{hendel_relative_2009} documents that the MLS market experiences a significant growth in recent years.} In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references. In-person interactions remain a vital aspect of the transaction process. Furthermore, the Chinese government imposes rigorous limitations on the upper and lower bounds of online listing prices, which has resulted in a reluctance among sellers to list their properties online. The regulatory environment permits real estate brokerages to occasionally post deceptive prices with the intention of attracting potential buyers, subsequently offering private information about other properties. Furthermore, the Chinese real estate brokerage market operates under a bilateral agency model, which results in a lower level of transaction efficiency when compared to the United States brokerage market. In Singapore, the real estate market is significantly influenced by government-coordinated prices and evaluation companies' suggested prices. Conversely, in China, sellers have greater autonomy to determine arbitrary listing prices in the offline market. It is a common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.

Even though the China's real estate brokerage market has traditionally been characterized by intense competition among offline stores, the advent of online platforms has dramatically reshaped the dynamics of real estate transactions. Brokerage consolidation, a process where larger firms absorb smaller ones into a unified platform, is emerging as a transformative trend, redefining how properties are bought and sold across China. Lianjia, the largest real estate brokerage in China, has revolutionized real estate transactions through the establishment of the Beke platform. This platform enables rapid expansion by integrating offline stores on a large scale while leveraging the advantages of resource sharing. However, prior to 2018, the platform Beke primarily focused on facilitating listings from Lianjia's offline stores and aimed to attract buyers from the market. In 2014, Beke introduced a strategic initiative called the Agent Cooperation Network (ACN), which aims to integrate and share resources across its various subsidiaries. This strategy enables the realization of multiple revenue streams simultaneously, thereby optimizing operational efficiency and enhancing overall economic performance.\footnote{The ACN model disaggregates the transaction process into specialized tasks handled by individual agents or stores. These tasks include seller-side activities such as sourcing sellers, maintaining property listings, commission negotiations, and buyer-side activities like client acquisition, property-client matching, transaction facilitation, and financial services assistance.} Furthermore, in 2018, Lianjia opted to augment its Agent Cooperation Network (ACN) strategy by integrating smaller brokerages into its network and inaugurating franchise stores under the Deyou brand, in addition to other smaller formats. This strategic maneuver was designed to augment network effects and further consolidate the platform, thereby enhancing market power and operational efficiency.

@@

In the context of the real estate market, it is evident that real estate is not a homogeneous good. Consequently, the brokerage market is distinguished by the presence of a considerable number of firms, exhibiting minimal barriers to entry. The prevailing economic theory posits that such a market, typified by robust competition, a multitude of firms, and a relatively low market concentration, is consistent with empirical observations. For instance, Lianjia's physical locations account for less than 5\% of the total, yet Lianjia handles approximately 20\% of the national transactions. Furthermore, numerous prominent agencies, such as Woaiwojia and Centaline Property Agency, operate within this market, indicating a monopolistic competitive environment.

Nevertheless, when examining local segmented markets, the monopolistic competition model appears to be less pertinent. In local markets, the surrounding neighborhoods exhibit a high degree of homogeneity with respect to community characteristics and the availability of public resources. In particular, apartments are the most favored property type in the Chinese real estate market, characterized by minimal inherent differences, making them relatively homogeneous goods. Furthermore, local real estate markets exhibit no barriers to entry or exit, closely resembling perfect competition. From a cost perspective, the real estate market has undergone platform-mediated reforms, whereby data resources exhibit zero marginal cost characteristics and operating costs decrease in line with the expansion of the user base. This suggests the presence of characteristics associated with a natural monopoly. In light of these circumstances, the operational stance of firms diverges considerably from that observed in a monopolistically competitive market. The presence of network effects gives rise to a virtuous cycle wherein an expansion in the number of branches of a dominant real estate agency draws in a greater number of users, which in turn attracts a greater volume of real estate listings. This positive feedback loop serves to reinforce the dominant position of firms like Lianjia, ultimately leading to the formation of oligopolistic firms. These oligopolistic firms are then able to sustain and reinforce their dominant market positions.

In local segmented markets, oligopolistic firms are responsible for increasing network strength and possess considerable market power. In segmented markets where some oligopolistic firms do not have strong network effects, multiple other firms serve the diverse needs of consumers and expand their scale. The real estate brokerage market is characterised by an inclusive competitive landscape, which can be attributed to a number of factors, including free entry, rapid technological progress and business model innovation. This environment allows oligopolistic firms to either enhance the strength of their network effects or face challenges to their dominant positions. Consequently, monopolistic structures emerge from and are subsequently disrupted by competition, thereby enabling real estate intermediaries to continuously evolve and drive the industry's rapid growth. In practical terms, this suggests that a competitive oligopolistic structure does not inherently impede competitive efficiency. Rather, as our empirical findings indicate, the enriched entry and transformations within the market lead to an increase in the number of transactions and house tours. This type of market structure can enhance firm efficiency, thereby facilitating more efficient transactions for buyers and sellers and improving overall market welfare, even though it may impede individual seller welfare. Moreover, this form of competition predominantly occurs among different brands within the larger platform, while the broader monopolistic or oligopolistic structure remains largely insulated from the competitive pressures posed by new entrants.

As evidenced by our empirical findings, Lianjia's strategic approach has markedly augmented its network strength within the context of segmented markets. From this perspective, the enhancement of network effects further drives the segmented market toward an oligopolistic competitive structure, which could increase market welfare and facilitate transactions between buyers and sellers. Furthermore, with the advent of online platforms and novel technologies, such as Lianjia's cutting-edge virtual reality (VR) home viewing technology, these network effects are gradually shifting from local networks to a global network. Consequently, this development is transforming the overall market into an oligopolistic competition model on a larger scale.

As network effects intensify in the future, the real estate brokerage market may witness a more pronounced consolidation of market power among a few dominant players. This consolidation may result in increased efficiencies through economies of scale and scope, whereby firms utilize their extensive data resources and technological advancements to optimize operations and enhance consumer experiences. Nevertheless, this transition gives rise to significant considerations for regulatory authorities, with a view to guaranteeing that the market remains competitive and accessible. The dynamic interplay between technological innovation and market structure will be of more crucial. As firms such as Lianjia persist in their efforts to innovate, incorporating artificial intelligence, big data analytics, and blockchain technology for secure transactions, the real estate market may become more transparent and efficient. Such developments could reduce transaction costs, diminish information asymmetry, and furnish consumers with more personalized services. Moreover, the global reach of network effects suggests that real estate brokerage markets across disparate regions may become more interconnected. This interconnectivity could facilitate cross-city or cross-province investments and diversify property portfolios for investors, thereby contributing to a more resilient real estate market.

In conclusion, the evolution of the real estate brokerage market towards an oligopolistic competition model, driven by network effects and technological advancements, presents both opportunities and challenges. Our empirical findings indicate that this type of market structure does not impede competitive efficiencies. However, policymakers and industry stakeholders must navigate this landscape carefully to harness the benefits of increased efficiency and innovation while safeguarding against potential market power abuses and ensuring equitable access for all participants. A balanced approach to these issues will be essential for sustaining long-term growth and enhancing overall market welfare in the real estate industry.
